Differentially Private Bayesian Inference

### 2018-05-14 main.tex
fix mistake

\begin{equation*}
\begin{split}
2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in ]\\
& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] + \delta \Big)\\
\end{split}
\end{equation*}

>>>>

\begin{equation*}
\begin{split}
2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \Big) + \delta\\
\end{split}
\end{equation*}
